Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
intro editing; subfigure

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{graphics}
\usepackage{fancyvrb}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{minted}
\usepackage{breqn}
\usepackage{subcaption}
%\usepackage{subfigure}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

@@

\begin{definition}[Base induction variable]
  A variable \textit{v} of integer type is a \emph{base induction
    variable} if it is the control variable of a ``for''
  loop,\footnote{Or equivalent in the source language, \eg{},
    \texttt{do} in Fortran for our implementation} incremented by $1$ per
iteration. The variable is marked as a base induction variable
only within the scope of the loop. Induction variables are ranged
over by $i$, $j$, $k$ throughout. Since we do not use non-base
(derived) induction variables we often simply say \emph{induction variable}.
\end{definition}

@@

Regions have as terminals the \emph{region constants}, denoted by
\term{reflexive}, \term{forward}, \term{backward}, or \term{centered}. Each
region constant except \term{reflexive} is given a depth parameter $n$ (natural
number greater than 0). Each receives a dimension identifier $d$ (also a
natural number greater than 0). Region constants specify that an array is read
from by a collection of indices which in the $d^{th}$ dimension are
neighbourhood indices ranging from $i + 0$ up to $i \pm n$ inclusively,
\eg{}, the following is a valid stencil, reading from \term{a} and writing to
\term{b}:
%%
\begin{minted}{fortran}
!= stencil forward(depth=2, dim=1) :: a
b(i, 0) = a(i, 0) + a(i+1, 0) + a(i+2, 0)
\end{minted}
%%
were \texttt{i} is an induction variable.  The stencil specification
is associated to the array variable \texttt{a}. Note that the second
dimension is fixed at a constant here.
A \term{backward} stencil
is similar but has negative neighbourhood indices, \eg{},
%
\begin{minted}{fortran}
!= stencil backward(depth=2, dim=1) :: a
b(i) = a(i) + a(i-1) + a(i-2)
\end{minted}
%
A \texttt{centered} stencil is a combination of \texttt{forward}
and \texttt{backward} stencils to the same depth, \eg{},
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1) :: a
b(i) = ( a(i) + a(i-1) + a(i+1) ) / 3.0
\end{minted}

\begin{figure}[t]
\begin{align*}
\def\arraystretch{1.2}
\setlength{\arraycolsep}{0.2em}
\newcommand{\dimTy}{\mathbb{D}}
\begin{array}{rl}
\nonterm{specification} ::= & \nonterm{regionDec} \mid \nonterm{specDec} \\
\nonterm{specDec} ::= & \term{stencil} \; \nonterm{spec} \;
                        \texttt{::} \; v
  \\
\nonterm{regionDec} ::= &  \texttt{region} \; \nonterm{rvar} \; \texttt{=} \;
                         \nonterm{region}\\[1em]
%\nonterm{spec} ::= & \nonterm{spatial} \mid \nonterm{temporal}
%\\[1em]
\nonterm{spec} ::= & [\nonterm{approx},] \; [\nonterm{mult},] \; \nonterm{region} \\
\nonterm{mult} ::= & \term{readOnce} \\
\nonterm{approx} ::= & \term{atMost} \; \mid \; \term{atLeast} \\[0.1em]
\nonterm{region} ::= & \\
\multicolumn{2}{l}{\qquad\qquad\;\;\; \stenFwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenBwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenCen{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenRefl{\dimTy}}  \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{region} \; \term{+} \; \nonterm{region}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{region} \; \term{*} \; \nonterm{region}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{rvar}}  \\[0.5em]
%\nonterm{temporal} ::= \; & \term{dependency} \; (v \; \{ , v \}) [, \texttt{mutual}]
%  \\[0.5em]
\dimTy ::= \; & \mathbb{N}_{>0} \\
\nonterm{rvar} ::= \; & [\text{\term{a}-\term{z}$\,$\term{A}-\term{Z}$\,$\term{0}-\term{9}}]+
\end{array}
\end{align*}
\caption{Specification syntax (EBNF grammar)}
\label{fig:syntax}
\end{figure}

@@

The sum of two regions $r \texttt{+} r'$ specifies that an array is
read using the neighbourhood indices described by either $r$ or
$r'$. It can be thought of as a disjunction of specifications. For
example, the following gives the specification for the five-point
stencil which is the sum of two compound \texttt{reflexive} and
\texttt{centered} regions in each dimension:
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1)*reflexive(dim=2) + centered(depth=1, dim=2)*reflexive(dim=1) :: a

b(i,j) = -4*a(i,j) + a(i-1,j) + a(i+1,j)
                   + a(i,j-1) + a(i,j+1)
\end{minted}
%%
Here the left hand side of \texttt{+} says when the second dimension
(induction variable $j$) is fixed at the origin, the first dimension
(induction variable $i$) accesses immediate vicinity of the origin.
The right hand side of \texttt{+} is similar but the dimensions are reversed.
This reflects the symmetry under rotation in the fivepoint stencil.

The product of two regions $r \texttt{*} r'$ specifies that the array
is read with neighbourhood indices drawn from the bounding box created
by the regions two regions $r$ and $r'$. For example, the following
code (defining a nine-point stencil) has a specification as the
product of two \texttt{centered} regions in each dimension:
%%
\begin{minted}[breakindent=2.9em]{fortran}
x = a(i, j)   + a(i-1, j)   + a(i+1, j)
y = a(i, j-1) + a(i-1, j-1) + a(i+1, j-1)
z = a(i, j+1) + a(i-1, j+1) + a(i+1, j+1)

!= stencil centered(depth=1, dim=1) * centered(depth=1, dim=2) :: a
b(i, j) = (x + y + z) / 9.0
\end{minted}
%%
Such a stencil computation is a common image convolution (for example
for edge detection).
Note that there are a number of intermediate assignments over which
the whole specification ranges.

The region constructor \texttt{*} can also be interpreted as conjunction of
two specifications since they need to hold simultaneously for their
corresponding dimensions.

As another example, the following code and specification
implements the \emph{Roberts cross}
edge-detection convolution~\cite{davis1975survey}:
%%
\begin{minted}[breakindent=5.5em]{fortran}
do j=0, jmax-1
    do i=0, imax-1
      x = a(i,j) - a(i+1,j+1)
      y = a(i+1,j) - a(i,j+1)
      != stencil forward(depth=1,dim=1) * forward(depth=1,dim=2) :: a
      b(i,j) = sqrt(x*x+y*y)
   end do
end do
\end{minted}

@@

Region specifications can be assigned to region variables via
a region declaration, which can be used later to form a spatial
specification. For example, the specification from the previous
 example can be restated as:
%%
\begin{minted}{fortran}
!= region r1 = centered(depth=1, dim=1)
!= region r2 = centered(depth=1, dim=2)
!= region robertsCross = r1*r2
!= stencil robertsCross :: a
\end{minted}
This is especially useful for common stencils such as Robert's cross
as the region can be defined once and used by region name many times.
%%
\paragraph{Spatial modifiers}
%%
There are two modifiers: one used at specification and the other at region
level to provide better descriptions for stencil computations.

@@

\begin{figure}
\vspace{-0.2em}
\begin{align*}
\setlength{\arraycolsep}{0.05em}
\begin{array}{c}
%\framebox{$\textit{region} \equiv \textit{region}'$} \\[0.7em]
\begin{array}{rll}
(\textsc{F\, \texttt{+} \,F}) \;\; &
\stenFwdSR{n \, \textsf{max} \, m}{d}{r \vee s} \\
 \equiv \; & \stenFwdSR{n}{d}{r} \; \texttt{+} \; \stenFwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{B\, \texttt{+} \,B}) \;\; &
\stenBwdSR{n \, \textsf{max} \, m}{d}{r \vee s} \\
 \equiv \; & \stenBwdS{n}{d}{r} \; \texttt{+} \; \stenBwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{C\, \texttt{+} \,C}) \;\; &
\stenCenSR{n \, \textsf{max} \, m}{d}{r \vee s} \\
\equiv \; & \stenCenSR{n}{d}{r} \; \texttt{+} \; \stenCenSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{C\, \texttt{+} \,F}) \;\; & \stenCenSR{n}{d}{r \vee s} \\
\textit{$m \leq n$} \; \equiv \; & \stenCenSR{n}{d}{r} \; \texttt{+} \;
                      \stenFwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{C\, \texttt{+} \,B}) \;\; &
\stenCenSR{n}{d}{r \vee s} \\
\textit{$m \leq n$} \; \equiv \; & \stenCenSR{n}{d}{r} \; \texttt{+} \;
                      \stenBwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{B\, \texttt{+} \,F}) \;\; &
\stenCenSR{n}{d}{r \vee s} \\
\equiv \; & \stenFwdSR{n}{d}{r} \; \texttt{+} \; \stenBwdSR{n}{d}{s}
  \\[0.7em]
%
%
(\textsc{R\, \texttt{+} \,F}) \;\; &
\stenFwdS{n}{d} \\
\equiv \; & \stenReflSR{d} \; \texttt{+} \; \stenFwdSR{n}{d}{r} \\[0.7em]
%
%
(\textsc{R\, \texttt{+} \,B}) \;\; &
\stenBwdS{n}{d} \\
\equiv \; & \stenReflSR{d} \; \texttt{+} \; \stenBwdSR{n}{d}{r} \\[0.7em]
%
%
(\textsc{R\, \texttt{+} \,C}) \;\; &
\stenCenS{n}{d} \\
\equiv \; & \stenReflSR{d} \; \texttt{+} \; \stenCenSR{n}{d}{r} \\[0.7em]
%
%
(\textsc{irrefl}) \;\; & (R \, \term{*} \, S^\irreflS) \, \term{+} \,
                         (R^\irreflS \, \term{*} \, S) \;
\equiv \; R \, \term{*} \, S \\[0.5em]
%
%
(\texttt{+}\textsc{idem}) \;\; & S \; \texttt{+} \; S \; \equiv \; S \\[0.5em]
%
(\texttt{+}\textsc{comm}) \;\; & S \; \texttt{+} \; T \; \equiv \; T \;
                       \texttt{+} \; S \\[0.5em]
%
(\texttt{+}\textsc{assoc}) \;\; & R \; \texttt{+} \; (S \; \texttt{+} \; T) \; \equiv \; (R \;
                       \texttt{+} \; S) \; \texttt{+} \; T \\[0.5em]
(\texttt{*}\textsc{comm}) \;\; & S \; \texttt{*} \; T \; \equiv \; T \;
                       \texttt{*} \; S \\[0.5em]
%
(\texttt{*}\textsc{assoc}) \;\; & R \; \texttt{*} \; (S \; \texttt{*} \; T) \; \equiv \; (R \;
                       \texttt{*} \; S) \; \texttt{*} \; T \\[0.5em]
(\textsc{dist}) \;\; & R \; \texttt{*} \; (S \; \texttt{+} \; T) \; \equiv \; (R \;
                       \texttt{*} \; S) \; \texttt{+} \; (R
                       \; \texttt{*} \; T)
\end{array}
%
%\framebox{${\textit{specDec} :: \texttt{v}} \equiv
%{\textit{specDec'} :: \texttt{v}}$} \\[0.7em]
%\begin{array}{rl}
% MUTUAL
%(\textsc{mutual}) \; &
%\texttt{stencil} \; \texttt{dependency} (\texttt{v}), \texttt{mutual}
%  :: \texttt{w}
%\\
%\equiv \; & \texttt{stencil} \; \texttt{dependency} (\texttt{w}), \texttt{mutual} ::
%  \texttt{v} \\[0.5em]
%(\textsc{coalesce}) \; &
%\texttt{stencil} \; \texttt{dependency} (\bar{v})
%  :: \texttt{v} \\
%& ; \texttt{stencil} \; \texttt{dependency} (\bar{w})
%  :: \texttt{v}
%\\
%\equiv \; & \texttt{stencil} \; \texttt{dependency} (\bar{v}, \bar{w}) ::
%  \texttt{v} \\[0.5em]
%\end{array}
\end{array}
\end{align*}
\caption{Equations on regions, $\textit{region} \equiv \textit{region}'$}
\label{fig:equations}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \subcaptionbox{\label{fig:jacobicorrect}}{\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  \subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  \subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  \subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \caption{Greyscale output of several perturbations of a Jacobi
    iteration program. The correct output is shown in
    (\subref{fig:jacobicorrect}).}
  \label{fig:jacobi}
\end{figure}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{graphics}
\usepackage{fancyvrb}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{minted}
\usepackage{breqn}
%\usepackage{subcaption}
\usepackage{subfigure}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

@@

\begin{definition}[Base induction variable]
  A variable \textit{v} of integer type is a \emph{base induction
    variable} if it is the control variable of a ``for''
  loop,\footnote{Or equivalent in the source language \eg{} 
    \texttt{do} in Fortran for our implementation.} incremented by $1$ per
iteration. The variable is marked as a base induction variable
only within the scope of the loop. Induction variables are ranged
over by $i$, $j$, $k$ throughout. Since we do not use non-base
(derived) induction variables we often simply say \emph{induction variable}.
\end{definition}

@@

Regions have as terminals the \emph{region constants}, denoted by
\term{reflexive}, \term{forward}, \term{backward}, or \term{centered}. Each
region constant except \term{reflexive} is given a depth parameter $n$ (natural
number greater than 0). Every region constant receives a dimension identifier $d$ (also a
natural number greater than 0). Region constants specify that an array is read
from by a collection of indices which in the $d^{th}$ dimension are
neighbourhood indices ranging from $i + 0$ up to $i \pm n$ inclusively,
\eg{}, the following is a valid stencil, reading from \term{a} and writing to
\term{b}:
%%
\begin{minted}{fortran}
!= stencil forward(depth=2, dim=1) :: a
b(i, 0) = a(i, 0) + a(i+1, 0) + a(i+2, 0)
\end{minted}
%%
were \texttt{i} is an induction variable.  The specification
is associated to the array variable \texttt{a}. Note that the second
dimension is constant.

The \term{forward},
\term{backward}, and \term{centered} regions can all receive an
additional optional attribute \term{irreflexive} which marks
that the region does not include the origin (offset 0).
For example, the following is a \term{backward} stencil, which is similar
to \term{forward} but has negative neighbourhood indices, and which
is irreflexive:
%
\begin{minted}{fortran}
!= stencil backward(depth=2, dim=1, irreflexive) :: a
b(i) = a(i-1) + a(i-2)
\end{minted}
%
A \texttt{centered} stencil is a combination of \texttt{forward}
and \texttt{backward} stencils to the same depth, \eg{},
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1) :: a
b(i) = ( a(i) + a(i-1) + a(i+1) ) / 3.0
\end{minted}

\begin{figure}[t]
\begin{align*}
\def\arraystretch{1.2}
\setlength{\arraycolsep}{0.2em}
\newcommand{\dimTy}{\mathbb{D}}
\begin{array}{rl}
\nonterm{specification} ::= & \nonterm{regionDec} \mid \nonterm{specDec} \\
\nonterm{specDec} ::= & \term{stencil} \; \nonterm{spec} \;
                        \texttt{::} \; v \\
\nonterm{regionDec} ::= &  \texttt{region} \; \nonterm{rvar} \; \texttt{=} \;
                         \nonterm{region}\\[0.4em]
%\nonterm{spec} ::= & \nonterm{spatial} \mid \nonterm{temporal}
%\\[1em]
\nonterm{spec} ::= & [\nonterm{approx},] \; [\nonterm{mult},] \; \nonterm{region} \\
\nonterm{mult} ::= & \term{readOnce} \\
\nonterm{approx} ::= & \term{atMost} \; \mid \; \term{atLeast} \\[0.1em]
\nonterm{region} ::= & \\
\multicolumn{2}{l}{\qquad\qquad\;\;\; \stenFwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenBwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenCen{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenRefl{\dimTy}}  \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{region} \; \term{+} \; \nonterm{region}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{region} \; \term{*} \; \nonterm{region}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{rvar}}  \\[0.5em]
%\nonterm{temporal} ::= \; & \term{dependency} \; (v \; \{ , v \}) [, \texttt{mutual}]
%  \\[0.5em]
\dimTy ::= \; & \mathbb{N}_{>0} \\
\nonterm{rvar} ::= \; & [\text{\term{a}-\term{z}$\,$\term{A}-\term{Z}$\,$\term{0}-\term{9}}]+\\[-1em]
\end{array}
\end{align*}
\caption{Specification syntax (EBNF grammar)}
\label{fig:syntax}
\end{figure}

@@

The product of two regions $r \texttt{*} r'$ specifies that an array
is read with neighbourhood indices drawn from the bounding box created
by the regions two regions $r$ and $r'$. For example, the following
code (defining a \emph{nine-point stencil}) has a specification given by the
product of two \texttt{centered} regions in each dimension:
%%
\begin{minted}[breakindent=2.9em]{fortran}
x = a(i, j)   + a(i-1, j)   + a(i+1, j)
y = a(i, j-1) + a(i-1, j-1) + a(i+1, j-1)
z = a(i, j+1) + a(i-1, j+1) + a(i+1, j+1)

!= stencil centered(depth=1, dim=1) * centered(depth=1, dim=2) :: a
b(i, j) = (x + y + z) / 9.0
\end{minted}
%%
This pattern is a common image convolution (for example
for edge detection). The specification ranges over the
values that flow the array subscript on the left-hand side,
and so ranges over the intermediate assignments to \term{x},
\term{y}, and \term{z}.

The region constructor \texttt{*} can also be interpreted as a
kind of conjunction on specifications since they constraint
indices to be within both regions simultaneously.

The sum of two regions $r \texttt{+} r'$ specifies that an array is
read using the neighbourhood indices described by either $r$ or
$r'$; it acts as a disjunction on specifications. For
example, the following gives the specification of a five-point
stencil which is the sum of two compound \texttt{reflexive} and
\texttt{centered} regions in each dimension:
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1)*reflexive(dim=2) + centered(depth=1, dim=2)*reflexive(dim=1) :: a
b(i,j) = -4*a(i,j) + a(i-1,j) + a(i+1,j)
                   + a(i,j-1) + a(i,j+1)
\end{minted}
%%
Here the left hand side of \texttt{+} says that when the second dimension
(induction variable $j$) is fixed at the origin, the first dimension
(induction variable $i$) accesses the immediate vicinity of the origin
(to depth of one). The right hand side of \texttt{+} is similar but the dimensions are reversed.
This reflects the symmetry under rotation of the five-point stencil.

As another example, the following 
implements and specifies the \emph{Roberts cross}
edge-detection convolution~\cite{davis1975survey}:
%%
\begin{minted}[breakindent=5.5em]{fortran}
do j=0, jmax-1
    do i=0, imax-1
      x = a(i,j) - a(i+1,j+1)
      y = a(i+1,j) - a(i,j+1)
      != stencil forward(depth=1,dim=1) * forward(depth=1,dim=2) :: a
      b(i,j) = sqrt(x*x+y*y)
   end do
end do
\end{minted}

@@

Region specifications can be assigned to region variables via
a region declaration, which can be used later to form a spatial
specification. For example, the specification from the previous
 example can be restated as:
%%
\begin{minted}{fortran}
!= region r1 = forward(depth=1, dim=1)
!= region r2 = forward(depth=1, dim=2)
!= region robertsCross = r1*r2
!= stencil robertsCross :: a
\end{minted}
This is especially useful for common stencil patterns, such as Roberts cross,
as the region can be defined once and reused.
%%
\paragraph{Spatial modifiers}
%%
There are two modifiers: one used at specification and the other at region
level to provide better descriptions for stencil computations.

@@

\begin{figure}
\vspace{-0.2em}
\begin{align*}
\setlength{\arraycolsep}{0.05em}
\begin{array}{c}
%\framebox{$\textit{region} \equiv \textit{region}'$} \\[0.7em]
\begin{array}{rll}
(\textsc{F\, \texttt{+} \,F}) \;\; &
\stenFwdSR{n \, \textsf{max} \, m}{d}{r \vee s} \\
 \equiv \; & \stenFwdSR{n}{d}{r} \; \texttt{+} \; \stenFwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{B\, \texttt{+} \,B}) \;\; &
\stenBwdSR{n \, \textsf{max} \, m}{d}{r \vee s} \\
 \equiv \; & \stenBwdSR{n}{d}{r} \; \texttt{+} \; \stenBwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{C\, \texttt{+} \,C}) \;\; &
\stenCenSR{n \, \textsf{max} \, m}{d}{r \vee s} \\
\equiv \; & \stenCenSR{n}{d}{r} \; \texttt{+} \; \stenCenSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{C\, \texttt{+} \,F}) \;\; & \stenCenSR{n}{d}{r \vee s} \\
\textit{$m \leq n$} \; \equiv \; & \stenCenSR{n}{d}{r} \; \texttt{+} \;
                      \stenFwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{C\, \texttt{+} \,B}) \;\; &
\stenCenSR{n}{d}{r \vee s} \\
\textit{$m \leq n$} \; \equiv \; & \stenCenSR{n}{d}{r} \; \texttt{+} \;
                      \stenBwdSR{m}{d}{s} \\[0.7em]
%
%
(\textsc{B\, \texttt{+} \,F}) \;\; &
\stenCenSR{n}{d}{r \vee s} \\
\equiv \; & \stenFwdSR{n}{d}{r} \; \texttt{+} \; \stenBwdSR{n}{d}{s}
  \\[0.7em]
%
%
(\textsc{R\, \texttt{+} \,F}) \;\; &
\stenFwdS{n}{d} \\
\equiv \; & \stenReflSR{d} \; \texttt{+} \; \stenFwdSR{n}{d}{r} \\[0.7em]
%
%
(\textsc{R\, \texttt{+} \,B}) \;\; &
\stenBwdS{n}{d} \\
\equiv \; & \stenReflSR{d} \; \texttt{+} \; \stenBwdSR{n}{d}{r} \\[0.7em]
%
%
(\textsc{R\, \texttt{+} \,C}) \;\; &
\stenCenS{n}{d} \\
\equiv \; & \stenReflSR{d} \; \texttt{+} \; \stenCenSR{n}{d}{r} \\[0.7em]
%
%
(\textsc{irrefl}) \;\; & (R \, \term{*} \, S^\irreflS) \, \term{+} \,
                         (R^\irreflS \, \term{*} \, S) \;
\equiv \; R \, \term{*} \, S \\[0.5em]
%
%
(\texttt{+}\textsc{idem}) \;\; & S \; \texttt{+} \; S \; \equiv \; S \\[0.5em]
%
(\texttt{+}\textsc{comm}) \;\; & S \; \texttt{+} \; T \; \equiv \; T \;
                       \texttt{+} \; S \\[0.5em]
%
(\texttt{+}\textsc{assoc}) \;\; & R \; \texttt{+} \; (S \; \texttt{+} \; T) \; \equiv \; (R \;
                       \texttt{+} \; S) \; \texttt{+} \; T \\[0.5em]
(\texttt{*}\textsc{comm}) \;\; & S \; \texttt{*} \; T \; \equiv \; T \;
                       \texttt{*} \; S \\[0.5em]
%
(\texttt{*}\textsc{assoc}) \;\; & R \; \texttt{*} \; (S \; \texttt{*} \; T) \; \equiv \; (R \;
                       \texttt{*} \; S) \; \texttt{*} \; T \\[0.5em]
(\textsc{dist}) \;\; & R \; \texttt{*} \; (S \; \texttt{+} \; T) \; \equiv \; (R \;
                       \texttt{*} \; S) \; \texttt{+} \; (R
                       \; \texttt{*} \; T)
\end{array}
%
%\framebox{${\textit{specDec} :: \texttt{v}} \equiv
%{\textit{specDec'} :: \texttt{v}}$} \\[0.7em]
%\begin{array}{rl}
% MUTUAL
%(\textsc{mutual}) \; &
%\texttt{stencil} \; \texttt{dependency} (\texttt{v}), \texttt{mutual}
%  :: \texttt{w}
%\\
%\equiv \; & \texttt{stencil} \; \texttt{dependency} (\texttt{w}), \texttt{mutual} ::
%  \texttt{v} \\[0.5em]
%(\textsc{coalesce}) \; &
%\texttt{stencil} \; \texttt{dependency} (\bar{v})
%  :: \texttt{v} \\
%& ; \texttt{stencil} \; \texttt{dependency} (\bar{w})
%  :: \texttt{v}
%\\
%\equiv \; & \texttt{stencil} \; \texttt{dependency} (\bar{v}, \bar{w}) ::
%  \texttt{v} \\[0.5em]
%\end{array}
\end{array}
\end{align*}
\caption{Equations on regions, $\textit{region} \equiv \textit{region}'$}
\label{fig:equations}
\end{figure}

@@

\begin{figure}[t]
  \centering
  %\subcaptionbox{\label{fig:jacobicorrect}}{\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \subfigure[]{\label{fig:jacobicorrect}\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \caption{Greyscale output of several perturbations of a Jacobi
    iteration program. The correct output is shown in
    (\subref{fig:jacobicorrect}).}
  \label{fig:jacobi}
\end{figure}
